Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-05 paper.tex
more introductions

How should we perform inference for the model
in~\ref{graphicalModel}(a)?  An intuitive strategy is to exploit the
conditional independence of the programs conditioned on the DSL, and
so to alternate between estimating the DSL ($\mathcal{D},\theta$) and
estimating a posterior distribution over the programs by searching for
programs written using the current DSL.  In practice searching the
space of programs is difficult, so we use the recognition model to
learn how to efficiently search for programs in the current DSL.

>>>>

How should we perform inference for the model
in~\ref{graphicalModel}(a)?  We take the intuitive strategy of exploiting the
conditional independence of the programs conditioned on the DSL, and
so alternate between estimating the DSL ($\mathcal{D},\theta$) and
estimating a posterior distribution over $p$ by searching for
programs written using $\mathcal{D}$.  In practice searching the
space of programs is difficult, so we use the recognition model to
learn how to efficiently search for programs.

We apply \system to four domains:
 building Boolean circuits; symbolic regression; FlashFill-style~\cite{gulwani2011automating} string processing problems; and Lisp-style functions on lists.
 For each of these we deliberately provide an impoverished
 set of programming primitives,
 and show that our algorithm discovers
 its own domain-specific vocabulary for expressing solutions in each of these domains (Table~\ref{initialExampleDSL}).
 \begin{table}
    \begin{tabular}{ll}
   \toprule
   Domain&Subset of induced DSL\\\midrule
   \\\bottomrule
 \end{tabular}
   \end{table}
